%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Business Intelligence Analyst} % Job title
{KUKA AG} % Organization
{Augsburg, Germany} % Location
{Jul 2024 - now} % Date(s)
{ % Description(s) of tasks/responsibilities
    \begin{cvitems}
    \item {Developed Power BI dashboards supporting monthly close \& financial reporting; enabled actionable insights for finance teams.}
    \item {Partnered with Finance \& Operations leaders to streamline reporting processes, improving accuracy and speed.}
    \item {Automated data retrieval \& transformation, cutting manual reporting effort by 40 \% }
    \item {Contributed to integration of finance data into the data lake, improving scalability of reporting.}
    \end{cvitems}
}


%------------------------------------------------


\cventry
{Head of Dashboarding \& Reporting} % Job title
{BBG GmbH} % Organization
{Berlin, Germany} % Location
{Aug.2022-Jul.2024} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Established \& led the BI \& Analytics function, aligning reporting across global teams.}
\item {Consolidated 600+ dashboards into 50, increasing usability and saving 100+ analyst hours monthly.}
\item {Designed and rolled out executive Power BI dashboards for C-level, Finance, Marketing, and Product.}
\item {Standardized BI governance (workspaces, gateways, sources), improving data reliability.}
\item {Collaborated with Data Engineering to optimize pipelines, ensuring scalable ELT processes.}
\item {Enabled self-service BI tools for cross-departmental teams, improving data accessibility.}
\end{cvitems}
}

%------------------------------------------------


\cventry
{Senior M&A Associate} % Job title
{BBG GmbH} % Organization
{Berlin, Germany} % Location
{Dec.2021 - Aug.2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Conducted financial due diligence and developed post-acquisition integration strategies.}
\item {Built Power BI reports to track acquired companies’ performance in real time.}
\end{cvitems}
}

%------------------------------------------------


\cventry
{Senior FP&A Manager } % Job title
{AUTO1 Group} % Organization
{Berlin, Germany} % Location
{Jun.2021 - Nov.2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Led a team managing payroll consolidation, controlling, and cash flow planning.}
\item {Developed a P\&L model for weekly EBITDA forecasting, improving transparency.}
\item {Automated payroll budgeting \& analysis with SQL + Power BI, reducing reporting cycle time.}
\end{cvitems}
}

%------------------------------------------------


\cventry
{FP&A Manager } % Job title
{AUTO1 Group} % Organization
{Berlin, Germany} % Location
{Feb.2020 - Jun 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Managed payroll budgeting \& forecasting across 10+ European markets.}
\item {Standardized payroll reporting, ensuring cross-entity comparability.}
\item {Developed a transfer pricing model for payroll to support tax compliance.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Transaction Services Associate (M&A Due Diligence)} % Job title
{KPMG} % Organization
{Tokyo, Japan} % Location
{2018 - 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Performed financial due diligence on multimillion-euro M\&A deals.}
\item {Delivered Red Flag reports and post-merger financial integration strategies.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Financial Management Consultant} % Job title
{KPMG} % Organization
{Tokyo, Japan} % Location
{2017-2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Led finance process standardization for a global bank, aligning US GAAP \& JP GAAP.}
\item {Supported ERP implementation for budgeting \& cost control in an automotive company.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Finance \& Operations Manager} % Job title
{Romax Technology Japan} % Organization
{Tokyo, Japan} % Location
{2016-2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Managed budgeting, forecasting \& cash flow.}
\item {Led ERP (Dynamics AX) rollout, streamlining finance operations.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Internal Financial Management Consultant} % Job title
{Inksystem Japan} % Organization
{Yokohama, Japan} % Location
{2014-2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Directed financial planning \& analysis for Japan office; ensured profitability.}
\item {Oversaw accounting, payroll, and compliance under Japanese regulations.}
\item {Launched \& managed Amazon \& Rakuten e-commerce channels.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Project Manager} % Job title
{Inksystem Ukraine} % Organization
{Kharkiv, Ukraine} % Location
{2013 - 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Conducted feasibility study \& budgeting for Japan office launch.}
\item {Oversaw planning and execution of international business expansion.}
\end{cvitems}
}

%------------------------------------------------


\end{cventries}
