%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Staff Software Engineer} % Job title
{Fernride Gmbh} % Organization
{Munich, Germany} % Location
{Sept. 2023 - now} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Low-level software development for safety ECU}
\item {Bootloader and saftey software development}
\item {Build system enhancement }
\item {Technical leadership of a subsystem development}
\item {Coordination with other teams and companies}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Senior Embedded Software Engineer} % Job title
{Argo AI Gmbh} % Organization
{Munich, Germany} % Location
{Feb. 2022 - July 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Integration of Autosar SWC to safety components of Autonomous Driving ECU}
\item {MCAL debug and development for Tricore and Xilinx MPSoC}
\item {Build system enhancement }
\item {Mentoring, interviewing}
\item {Projects: Argo SDS, Argo Lidar}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Embedded Software Engineer} % Job title
{ESR Labs Gmbh } % Organization
{Munich, Germany} % Location
{Aug. 2018 - Jan. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Dvelopment of drivers for PowerPC/ARM/Tricore-based MCUs}
\item {Bringup of new ECUs (done ~3-4 times)}
\item {Development of HIL testing tools}
\item {Development of internally used PCBs}
\item {Projects: CCP2022 (currently in development), ENS2021 (in SOP), RAM Booster 2021, CGW3 (in SOP)}
\end{cvitems}
}
%------------------------------------------------    

\cventry
{Firmware Developer} % Job title
{Wayray} % Organization
{Moscow, Russia} % Location
{Mar. 2018 - June. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Development of internal automotive embedded tools (STM32-based)}
\item {Development of C\#-based GUI tool for remote control of climate tests chamber}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Embedded Software Engineer(part/full-time)} % Job title
{ITELMA} % Organization
{Moscow, Russia} % Location
{Nov. 2016 - Mar. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Development of low-level software for russian automotive (VAZ, KamAZ, GAZ, UAZ) - PowerPC/XC1xxx-based.}
\item {Development of HIL testing equipment}
\item {Development of CI pipeline}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Embedded Design Engineer (part-time)} % Job title
{Alter LTD} % Organization
{Moscow, Russia} % Location
{Nov. 2015 - Nov. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Development of audible altimeter - schematics/PCB design, firmware development, bootloader }
\item {Support for visual altimeter}
\item {Support in assembling the altimeters (SMD soldering) and in debug of broken altimeters}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Junior Java Developer (part-time)} % Job title
{NetCracker LLC} % Organization
{Moscow, Russia} % Location
{Mar. 2015 - Nov. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Development of Java/SQL OSS service (Customer Billing Management) for telecom providers}
\end{cvitems}
}

\end{cventries}