%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Staff Software Engineer} % Job title
{Fernride Gmbh} % Organization
{Munich, Germany} % Location
{Sept. 2023 - now} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Low-level software development for safety ECU}
\item {Bootloader and saftey software development}
\item {Build system enhancement }
\item {Technical leadership of a subsystem development}
\item {Coordination with other teams and companies}
\end{cvitems}
}


%------------------------------------------------

\cventry
{Senior Embedded Software Engineer} % Job title
{Argo AI Gmbh} % Organization
{Munich, Germany} % Location
{Feb. 2022 - Jul.2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Integration of Autosar SWC to safety components of Autonomous Driving ECU}
\item {MCAL debug and development for Tricore and Xilinx MPSoC}
\item {Build system enhancement }
\item {Mentoring, interviewing}
\item {Projects: Argo SDS, Argo Lidar}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Senior Embedded Software Engineer} % Job title
{ESR Labs Gmbh} % Organization
{Munich, Germany} % Location
{Mar.2021 - Jan.2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Support of whole driver infrastructure for TC3xx MCU family}
\item {Architecture of all low-level software for motorcycle ECU}
\item {Development of HIL testing tools for internal use}
\item {Bring up of new ECUs prior to development}
\end{cvitems}
}

\cventry
{Embedded Software Engineer} % Job title
{ESR Labs AG} % Organization
{Munich, Germany} % Location
{Aug. 2018 - Mar.2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Development of drivers for automotive MCUs}
\item {Development of small-series PCB devices for internal use}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Firmware Developer} % Job title
{Wayray} % Organization
{Moscow, Russia} % Location
{Mar. 2018 - June. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Development of internal automotive embedded tools.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Embedded Software Engineer} % Job title
{ITELMA} % Organization
{Moscow, Russia} % Location
{Nov. 2016 - Mar. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Development of low-level software for russian automotive (VAZ, KamAZ, GAZ, UAZ).}
\item {Development of HIL testing equipment}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}